---
title: "Linear Regression in R"
output:
  html_document:
    df_print: paged
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(DataExplorer)
library(fastDummies)
library(caTools)
library(Metrics)
```
## Fish Weight Prediction

This dataset is a record of 7 common different fish species in fish market sales. With this dataset, a predictive model can be performed using machine friendly data and estimate the weight of fish can be predicted.

<h3>1. Data Exploration</h3>
First input and see the structure of the dataset:
```{r}
data_fish <-  read.csv("Fish.csv")
names(data_fish)[1] = "Species"
str(data_fish)
```
To do the linear regression in this dataset, the Species feature need to convert to dummy variables. Structure after dummy:
```{r}
data_fish = dummy_cols(data_fish)
data_fish = data_fish[,-1]
str(data_fish)
```
<h3>2. Missing values</h3>
```{r}
plot_missing(data_fish)
```
</br>It is good that, the dataset is not have missing values.
<h3>3. Correlation</h3>
```{r}
plot_correlation(data_fish)
```
</br>From the plot, it show that the Length 1, Length 2, Length 3, Height and Width feature have a high correlation on the Weight feature
<h3>4. Stratified sampling</h3>
The sampling will divide the dataset so that 70% instanses of the dataset will go for training and 30% will go for validating
```{r, echo=FALSE}
set.seed(123)
split <- sample.split(data_fish$Weight, SplitRatio = 0.7)
training_set = subset(data_fish, split == TRUE)
test_set = subset(data_fish, split == FALSE)
```
```{r}
str(training_set)
str(test_set)
```
<h3>5. Linear Regression Model</h3>
```{r}
regressor = lm(formula = Weight ~ .,
               data = training_set)
summary(regressor)
plot(regressor)
```
</br>The Residuals vs Fitted Plot show a slight parabola indicate that relationship between predictor variables and target variable (weight) maybe is slight non-linear relationship. 
</br>The QQ Plot show that the errors is almost normally distributed. 
</br>The Scale-Location Plot show that the residuals are spread equally along the range of predcitor.
</br>Residuals vs Leverage Plot show that there is no outlier that influent the regression result.
<h3>5. Predicting Result</h3>
```{r}
pred_test <- predict(regressor, test_set)
combine_table <- cbind(pred_test,test_set$Weight)
colnames(combine_table) <- c("Prediction Weight", "Real Weight")
combine_table
```
```{r, echo=TRUE}
pred_train = predict(regressor, training_set)
rmse_train <- sqrt(mean((training_set$Weight-pred_train)^2))
rmse_test <- sqrt(mean((test_set$Weight-pred_test)^2))

rss_train <- sum((training_set$Weight-pred_train)^2)
rss_test <- sum((test_set$Weight-pred_test)^2)

tss_train <- sum((training_set$Weight - mean(training_set$Weight)) ^ 2)
tss_test <- sum((test_set$Weight - mean(test_set$Weight)) ^ 2)

r_square_train <- 1-(rss_train/tss_train)
r_square_test <- 1-(rss_test/tss_test)
```
RMSE, RSS and R&#178; on the training set and test set:
<table class="table table-bordered" style="margin-left: auto; margin-right: auto;">
<thead>
<tr>
<th style="border-bottom:hidden; padding-bottom:0; padding-left:3px;padding-right:3px;text-align: center; " colspan="2">
<div style="border-bottom: 1px solid #ddd; padding-bottom: 5px; ">
RMSE
</div>
</th>
<th style="border-bottom:hidden; padding-bottom:0; padding-left:3px;padding-right:3px;text-align: center; " colspan="2">
<div style="border-bottom: 1px solid #ddd; padding-bottom: 5px; ">
RSS
</div>
</th>
<th style="border-bottom:hidden; padding-bottom:0; padding-left:3px;padding-right:3px;text-align: center;" colspan="2">
<div style="border-bottom: 1px solid #ddd; padding-bottom: 5px; ">
R&#178;
</div>
</th>
</tr>
<tr>
<th style="text-align:right;">
On training set
</th>
<th style="text-align:right;">
On test set
</th>
<th style="text-align:right;">
On training set
</th>
<th style="text-align:right;">
On test set
</th>
<th style="text-align:right;">
On training set
</th>
<th style="text-align:right;">
On test set
</th>
</tr>
</thead>
<tbody>
<tr>
<td style="text-align:right;">
85.85008
</td>
<td style="text-align:right;">
104.2211
</td>
<td style="text-align:right;">
818096.2
</td>
<td style="text-align:right;">
521377.6
</td>
<td style="text-align:right;">
0.9448807
</td>
<td style="text-align:right;">
0.9010514
</td>
</tr>
</tbody>
</table>
<h3>6. Conclusion</h3>
The R&#178; is reached at 0.9010514, which is a good figure as it very near 1 - the maximum value of R&#178;. It show that the predicted values is highly accurate even the The Residuals vs Fitted Plot shows the slight non-linear relationship between the predictor variables and target variable.